Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-24 10-conclusions.tex
wave form -> waveform.
Updates to conclusions.

Our sensor network provides real-time, two way communication between the sensor nodes (OPQ Boxes) and their cloud services, providing several innovative features for power quality monitoring. The OPQ triggering system exploits temporal locality to request high fidelity data from neighboring boxes when one exceeds a threshold, enabling our network to detect and analyze data that would have been unreported by a naive, threshold-based approach. The OPQ Information Architecture enables Actors at the Phenomena Layer to control sensitivity settings of individual OPQ Boxes in order to improve data collection when power quality anomalies have been predicted.

Our sensor network is designed to efficiently use network and storage resources. Two way communication enables OPQ Boxes to send low fidelity summary statistics on power quality at one second intervals, which can be used by cloud-based services to decide whether or not to request high fidelity data.  Our TTL mechanism implements a "use it or lose it" approach to cloud-based data, which in our pilot study reduced cloud storage requirements by over ten-fold.

>>>>

Our sensor network provides real-time, two-way communication between the sensor nodes (OPQ Boxes) and their cloud services, providing several innovative features for power quality monitoring. The OPQ triggering system exploits temporal locality to request high fidelity data from neighboring boxes when one exceeds a threshold, enabling our network to detect and analyze data that would have been unreported by a naive, threshold-based approach. The OPQ Information Architecture enables Actors at the Phenomena Layer to control sensitivity settings of individual OPQ Boxes in order to improve data collection when power quality anomalies have been predicted.
`
Our sensor network is designed to efficiently use network and storage resources. Two way communication enables OPQ Boxes to send low fidelity summary statistics on power quality at one second intervals, which can be used by cloud-based services to decide whether to request high fidelity data.  Our TTL mechanism implements a "use it or lose it" approach to cloud-based data, which in our pilot study reduced cloud storage requirements by over ten-fold.
